---
title: "Hello Julia"
author: "Eric Stern"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Testing Julia

I recently used julia is speed up a chunk of code over 2 hundred fold and was quite impressed. Since Julia is availible in R notebooks, I wanted to spend a little time experimenting.

## What is Julia

Julia is a relatively new language purpose built for data science. The reason it has a lot of appeal is that it is fast. And not even fast compared to other data science languages like R or Python; fast compared to Scala or C++. In a microbenchmark by the Julia Core team, Julia clocked a benchmark [comparable to C](https://julialang.org/benchmarks/). The benefits of Julia over languages like C++ or C is that there is very little boiler plate code due to it's optional typing. The syntax is closer to R than to C++. 

## Quick Note

I will be using an R notebook to write Julia using the `JuliaCall` package to manage to the translation. We can also use JuliaCall to write R code, similar to how you would use RCPP or reticulate.

## The Basics

```{julia}
a = sqrt(2); # minimal example
```

RMarkdown uses JuliaCall - an R package that performs translation between R and Julia Types. It does pretty well. For instance we can take a character vector and send it to julia using `julia_assign`.

```{r}
library(JuliaCall)

julia_assign(x = 'fizzbuzz', value = c('foo', 'fizz', 'buzz'))
```

This gets translated into a 1d array of strings in julia:

```{julia}
fizzbuzz
```

## Toy Analysis

Using `mtcars` lets build a quick modelling pipeline in julia. First we have to import a few packages. Julia uses the command `using` to load libraries.

```{julia}
using DataFrames, GLM
```

Now we can use `JuliaCall` to load some data into DataFrames in Julia.

```{r}
julia_assign('mtcars', mtcars)
```

This R function assigns the R dataframe object to a julia dataframe object called 'mtcars'. 
## Modelling

Now back in julia, let's do some work with dataframes, build some plots, and eventually run a model.

### Summary Statistics

`describe` is similar to R's `summary` function but returns a dataframe rather than a list.

```{julia}
describe(mtcars)
```


### Plotting

```{julia}
#import Pkg; Pkg.add("StatsPlots")
using StatsPlots: @df; using IndexedTables;
@df mtcars scatter(
    :mpg,
    :hp)

```



```{julia}

lm_mod = fit(LinearModel, @formula(mpg ~ hp + wt + qsec), mtcars)

```

